Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-15 paper/paper.tex
4.3.4

\tname\ uses the frequency of content modifiers to discriminate more
or less likely rules. For example, historical data indicates that
content options that use the \CodeIn{http\_connection} modifier are
much less likely than content options that use the modifier
\CodeIn{http\_uri}. Figure~\ref{fig:distribution-content_modifiers}
shows the histogram of content modifiers for http. Although content
modifiers are applicable to rules of any protocol in Suricata,
currently, \tname\ only supports tcp and http. These are the protocols
involving ~80\% of the attacks.

@@

Consider a rule containing the option \CodeIn{content:
  ``/HtmlAdaptor''}. The contribution of this option to the score of
the corresponding rule would be $0.5$
(=$\frac{10,111}{10,111*1}$). The value of $M_i$ for this case is 1 as
the field of the HTTP message \CodeIn{Request URI}---holding the
string ``/HtmlAdaptor''---can be accessed through the modifier
\CodeIn{http\_uri}. Conceptually, the relatively high heuristic value
given to this option indicates that this is a reasonable option
because the string used in the content option (``/HtmlAdaptor'') is
stored in a specific field of the HTTP message (\CodeIn{Request URI})
and can be accessible through content modifiers
(\CodeIn{http\_uri}). For the option \CodeIn{content: ``keep-alive''},
either \CodeIn{http\_header} or \CodeIn{http\_coxnnection} could be
used as modifier to locate the string ``keep-alive'' stored in the
field \CodeIn{Connection} (see Figure~\Fix{xxx}). Consequently, for
this case, the contribution of modifiers to this content option would
be $0.2$ (=$\frac{4089+29}{10111*2}$). Assuming that both options are
used in a rule, the aggregated contribution of this heuristic function
would be 0.35 (=(0.2+0.5)/2).

>>>>

\tname\ uses the frequency of content modifiers to discriminate more
or less likely rules. For example, historical data indicates that
content options that use the \CodeIn{http\_connection} modifier are
much less likely than content options that use the modifier
\CodeIn{http\_uri}. Figure~\ref{fig:distribution-content_modifiers}
shows the histogram of content modifiers for http. Although content
modifiers are applicable to rules of any protocol in Suricata,
currently, \tname\ only supports tcp and http. These are the protocols
involving ~80\% of the attacks. \Luc{80\% das regras do nosso dataset.}

@@

Consider a rule containing the option \CodeIn{content:
  ``/HtmlAdaptor''}. The contribution of this option to the score of
the corresponding rule would be $0.5$
(=$\frac{10,111+11}{10,111*2}$). The value of $M_i$ for this case is 2 as
the field of the HTTP message \CodeIn{Request URI}---holding the
string ``/HtmlAdaptor''---can be accessed through the modifiers
\CodeIn{http\_uri} and \CodeIn{http\_request\_line} \Luc{Inclui esse modificador pq ele tambem pode acessar o campo Request URI. Isso eh um problema? O http\_uri eh o modificador mais comum, mas o fato de haver o modificador http\_request\_line que tambem accessa a mesma posição faz com que o fitness maximo seja 0.5, pois a ocorrencia de http\_request\_line eh irrelevante no calculo.}. Conceptually, the relatively high heuristic value
given to this option indicates that this is a reasonable option
because the string used in the content option (``/HtmlAdaptor'') is
stored in a specific field of the HTTP message (\CodeIn{Request URI})
and can be accessible through content modifiers
(\CodeIn{http\_uri} and \CodeIn{http\_request\_line}). For the option \CodeIn{content: ``keep-alive''},
either \CodeIn{http\_header} or \CodeIn{http\_connection} could be
used as modifier to locate the string ``keep-alive'' stored in the
field \CodeIn{Connection} (see Figure~\Fix{xxx}). Consequently, for
this case, the contribution of modifiers to this content option would
be $0.2$ (=$\frac{4089+29}{10111*2}$). Assuming that both options are
used in a rule, the aggregated contribution of this heuristic function
would be 0.35 (=(0.2+0.5)/2).
